elasticnet

### 2022-06-15 analysis/elasticnet.Rmd
feat: add analysis of complete cases

```{r elasticnet_setup, message = FALSE}
library("targets")
library("ameld")
library("viridisLite")
tar_load(arcvob)
tar_load(bootrcv)
tar_load(bootarcv)
#tar_load(bootarcv9)
tar_load(amelddata)
tar_load(ameldcfg)
tar_load(zlog_data)
```

@@

@@

## arcv9.glmnet

```{r bootarcv9}
#a <- c(table(sapply(bootarcv9$models, function(m)m$fit$alpha)))
#plot(bootarcv9 , what = "calibration")
#plot(bootarcv9, what = "selected")
#plot_dots(a, main = "Selected Alpha Values")
```

>>>>

```{r elasticnet_setup, message = FALSE}
library("targets")
library("ameld")
library("viridisLite")
tar_load(arcvob)
tar_load(bootrcv)
tar_load(bootrcvcc)
tar_load(bootarcv)
tar_load(bootrcv.woIC)
tar_load(amelddata)
tar_load(amelddatacc)
tar_load(ameldcfg)
tar_load(zlog_data)
tar_load(zlog_data_complete_cases)
```

@@

## rcv.glmnet (complete cases only)

```{r bootrcvcc}
plot(bootrcvcc, what = "calibration")

ps <- lapply(
    zlog_data_complete_cases[paste0("SurvProbMeld", c("Unos", "NaUnos", "Plus7"))],
    function(p) {
        ctpnts <- cutpoints(p, n = ameldcfg$m)
        f <- cut(p, ctpnts, include.lowest = TRUE)
        list(
            predicted = groupmean(p, f = f),
            observed = observed_survival(
                amelddatacc$y, f = f, times = ameldcfg$times
            )
        )
    }
)
names(ps) <- c("MELD", "MELD-Na", "MELD-Plus7")
col <- viridisLite::viridis(6)[4:6]

plot(bootrcvcc, what = "selected", cex = 0.5)
plot(bootrcvcc$fit$glmnet.fit, xvar = "norm")
plot(bootrcvcc$fit$glmnet.fit, xvar = "lambda")
plot(bootrcvcc$fit$glmnet.fit, xvar = "dev")
```

## bootrcv.woIC

Exclude IL-6 and CYSC columns from the data set.

```{r bootrcv.woIC}
plot(bootrcv.woIC, what = "calibration")
plot(bootrcv.woIC, what = "selected", cex = 0.5)
```

@@
